%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
  \textbf{\Huge \scshape \hspace*{20pt} Curriculum vitae \hfill \LARGE Matej Troják \hspace*{20pt}} \\ \vspace{3pt}
  \small
  \faGlobe \hspace{.5pt} \href{https://xtrojak.github.io}{Portfolio}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/xtrojak}{GitHub}
  $|$
  \faLinkedinSquare \hspace{.5pt} \href{https://linkedin.com/in/matej-troj%C3%A1k-3b1229179}{LinkedIn}
  $|$
  \faEnvelopeO \hspace{.5pt} \href{mailto:mato.trojak@gmail.com}{mato.trojak@gmail.com}
  $|$
  \faMobile \hspace{.5pt} \href{tel:4917666014928}{+49 176 66014928}
  $|$
  \faMapMarker \hspace{.5pt} \href{https://goo.gl/maps/rqsk3bDELMWajqJe9}{Heidelberg, Germany}
\end{center}


%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart

  \resumeSubheading
  {Masaryk University
  % \normalfont{(Admission rate: 0.85\%)}
  }{Brno, Czech Republic}
  {PhD in Fundamentals of Computer Science (\href{https://is.muni.cz/th/m3qym/?lang=en}{thesis})}{2018 \textbf{--} 2023}

  \resumeSubSubheading{doctor of natural sciences conferred in Artificial intelligence and data processing (\href{https://is.muni.cz/auth/th/lc8hj/?lang=en}{thesis})}{2020}

  \resumeSubSubheading{master's degree conferred in Bioinformatics and systems biology (\href{https://is.muni.cz/th/lgs7n/?lang=en;setlang=en}{thesis})}{2015 \textbf{--} 2018}

  \resumeSubSubheading{bachelor's degree conferred in Bioinformatics and systems biology (\href{https://is.muni.cz/th/nhf6y/?lang=en;setlang=en}{thesis})}{2012 \textbf{--} 2015}

  
  \resumeSubHeadingListEnd


%----------- WORK EXPERIENCE -----------

\section{Work and Research Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

  \resumeSubheading
  {\href{https://www.embl.org/sites/heidelberg/}{EMBL}}{Heidelberg, Germany}
  {Planetary Biology Biocurator}{08/2023 \textbf{--} present}
  \small{
    \begin{itemize}
      \item curation and processing of metadata for \href{https://www.embl.org/about/info/trec}{\color{blue}TREC} (Traversing European Coastlines) project
      \item \textbf{formHTR} $|$ \href{https://github.com/grp-bork/formHTR}{\color{blue}\texttt{GitHub}} 
      \vspace{-2pt}
      \begin{itemize}
        \item[-] Handwritten text recognition in form documents \vspace{-2pt}
      \end{itemize}
    \end{itemize}
  }

  \vspace{10pt}

  \resumeSubheading
  {\href{https://www.recetox.muni.cz/en/services/data-services-1/spectrometric-data-processing-and-analysis}{Recetox}}{Brno, Czech Republic}
  {IT specialist}{06/2021 \textbf{--} 07/2023}
  \small{
    \begin{itemize}
      \item spectrometric data processing and analysis
      \item development of Galaxy tools and Galaxy administration
      \item \textbf{MSMetaEnhancer} $|$ \href{https://github.com/RECETOX/MSMetaEnhancer}{\color{blue}\texttt{GitHub}} \vspace{-2pt}
      \begin{itemize}
        \item[-] tool for semi-automatic mass spectra metadata annotation \vspace{-2pt}
        \item[-] mines multiple online databases and services for available data \vspace{-2pt}
      \end{itemize}
      \item \textbf{Galaxy tools} $|$ \href{https://github.com/RECETOX/galaxytools}{\color{blue}\texttt{GitHub}} \vspace{-2pt}
      \begin{itemize}
        \item[-] development of Galaxy tools for analysis of mass spectra data \vspace{-2pt}
        \item[-] administration of \href{https://umsa.cerit-sc.cz/}{UMSA} Galaxy instance \vspace{-2pt}
      \end{itemize}
    \end{itemize}
  }

  \vspace{10pt}

  \resumeSubheading
  {\href{http://czechglobe.cz/en/}{CzechGlobe}}{Brno, Czech Republic}
  {researcher and software developer}{02/2018 \textbf{--} 02/2022}
  \small{
    \begin{itemize}
      \item development of a platform to semi-automatise experimentation using photobioreactors (BioArInEO)
      \item \textbf{DeviceControl} $|$ \href{https://github.com/SmartBioTech/DeviceControl}{\color{blue}\texttt{GitHub}} \vspace{-2pt}
      \begin{itemize}
        \item[-] unified interface to control and measure data in specific cultivation devices \vspace{-2pt}
        \item[-] developed as a Python package for multiple platforms \vspace{-2pt}
      \end{itemize}
    \end{itemize}
  }

  \vspace{10pt}
    
  \resumeSubheading
  {\href{https://sybila.fi.muni.cz/}{Sybila}}{Brno, Czech Republic}
  {systems biology researcher}{09/2014 \textbf{--} 07/2023}
  \small{
    \begin{itemize}
      \item development of formal methods in computer science with application to systems biology \vspace{-2pt}
      \item a rule-based language called BioChemical Space language \vspace{2pt}
      \item \textbf{eBCSgen} $|$ \href{https://github.com/sybila/eBCSgen}{\color{blue}\texttt{GitHub}} \vspace{-2pt}
      \begin{itemize}
        \item[-] software tool developed in Python \vspace{-2pt}
        \item[-] maintenance and analysis of rule-based models \vspace{-2pt}
        \item[-] distributed using bioconda and a series of Galaxy tools
      \end{itemize}
      \item \textbf{e-cyanobacterium} $|$ \href{https://www.e-cyanobacterium.org/}{\color{blue}\texttt{WebPage}} \vspace{-2pt}
      \begin{itemize}
        \item[-] an instance of Comprehensive modelling platform \vspace{-2pt}
        \item[-] models and experiments online repository targeting cyanobacteria processes \vspace{-2pt}
      \end{itemize}
      \item \textbf{Galaxy tools} $|$ \href{https://github.com/sybila/galaxytools}{\color{blue}\texttt{GitHub}} \vspace{-2pt}
      \begin{itemize}
        \item[-] development of Galaxy tools for analysis of biochemical models \vspace{-2pt}
        \item[-] administration of \href{https://biodivine-vm.fi.muni.cz/galaxy}{Biodivine} Galaxy instance \vspace{-2pt}
      \end{itemize}
      \item \textbf{mypPBR} $|$ \href{https://github.com/xtrojak/bioreactor}{\color{blue}\texttt{GitHub}} \vspace{-2pt}
      \begin{itemize}
        \item[-] minimalistic yet professional open-source low-budget photobioreactor \vspace{-2pt}
      \end{itemize}
    \end{itemize}
  }

  \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming:}{ Python, R, MySQL, \LaTeX, MATLAB} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Git, Unix, Galaxy, Conda} \\ \vspace{3pt}
        
        \textbf{Languages:}{ Slovak (Native), English (Professional), German (Elementary)} \\ \vspace{3pt}
        
        \textbf{Teaching and tutoring:}{ two semesters of seminar tutoring at IB111: Foundations of Programming in Python; supervision (5) and reviews (16) of bachelor's and master's theses}
    }}
  \resumeSubHeadingListEnd


%----------- Publications -----------

\section{Publications}
\vspace{2pt}
\small{
  \begin{itemize}
    \item Matej Troják, David Šafránek, Samuel Pastva, and Luboš Brim. \textbf{Rule-based Modelling of Biological Systems Using Regulated Rewriting}. \emph{BioSystems} (225), Elsevier, 2023.
    \item Matej Troják, David Šafránek, Branislav Brozmann, and Luboš Brim. \textbf{eBCSgen 2.0: Modelling and Analysis of Regulated Rule-Based Systems}. Proceedings of the 20th \emph{International Conference on Computational Methods in Systems Biology} (\textbf{CMSB}), p. 302-309, LNBI 13447, Springer, 2022.
    \item Matej Troják, Helge Hecht, Martin Čech, and Elliott James Price. \textbf{MSMetaEnhancer: A Python package for mass spectra metadata annotation}. \emph{Journal of Open Source Software} 7(79), 2022.
    \item Matej Troják, David Šafránek, Lukrécia Mertová, and Luboš Brim. \textbf{eBCSgen: A Software Tool for Biochemical Space Language}. Proceedings of the 18th \emph{International Conference on Computational Methods in Systems Biology} (\textbf{CMSB}), p. 356-361, LNBI 12314, Springer, 2020.
    \item Matej Troják, David Šafránek, Lukrécia Mertová, and Luboš Brim. \textbf{Executable Biochemical Space for Specification and Analysis of Biochemical Systems}. \emph{PLoS ONE} 15(9), Public Library of Science, 2020.
    \item Matej Troják, David Šafránek, Luboš Brim, Jakub Šalagovič, and Jan Červený. \textbf{Executable Biochemical Space for Specification and Analysis of Biochemical Systems}. Proceedings of the 9th \emph{International Workshop on Static Analysis and Systems Biology} (\textbf{SASB}), p. 91-116, ENTCS 350, Elsevier, 2018.
    \item Matej Troják, David Šafránek, Lukrécia Mertová, and Luboš Brim. \textbf{Parameter Synthesis and Robustness Analysis of Rule-Based Models}. Proceedings of the 12th \emph{NASA Formal Methods} (\textbf{NFM}), p. 41-59, LNCS 12229, Springer, 2020.
    \item David, Šafránek, Matej Troják, Vojtěch Brůža, Tomáš Vejpustek, Jan Papoušek, Martin Demko, Samuel Pastva, Aleš Pejznoch, and Luboš Brim. \textbf{Barbaric Robustness Monitoring Revisited for STL* in Parasim}. Proceedings of the 17th \emph{International Conference on Computational Methods in Systems Biology} (\textbf{CMSB}), p. 356-359, LNBI 11773, Springer, 2019. 
    \item Nikola Beneš, Luboš Brim, Jan Červený, Samuel Pastva, David Šafránek, Jakub Šalagovič, and Matej Troják. \textbf{Fully Automated Attractor Analysis of Cyanobacteria Models}. Proceedings of the 22nd \emph{International Conference on System Theory, Control and Computing} (\textbf{ICSTCC}), p. 354-359, IEEE, 2018.
    \item Matej Troják, David Šafránek, Jakub Hrabec, Jakub Šalagovič, Františka Romanovská, and Jan Červený. \textbf{E-Cyanobacterium.org: A Web-Based Platform for Systems Biology of Cyanobacteria}. Proceedings of the 14th \emph{International Conference on Computational Methods in Systems Biology} (\textbf{CMSB}), p. 316-322, Springer, 2016.
    \item Tadeáš Děd, David Šafránek, Matej Troják, Matej Klement, Jakub Šalagovič, and Luboš Brim. \textbf{Formal Biochemical Space with Semantics in Kappa and BNGL}. Proceedings of the 6th \emph{International Workshop on Static Analysis and Systems Biology} (\textbf{SASB}), p. 27-49, Elsevier, 2015.
  \end{itemize}
}


%-------------------------------------------
\end{document}
